### 2019-08-23 ch1_introduction.tex
update

@@

	\centering\fontsize{9}{11}\selectfont
	\begin{tabularx}{\linewidth}{|p{2cm}lllX|}
		\hline
		Name & Role & Repo & Downloads p.a. & Description \\ \hline\hline
		babelwhale & aut & CRAN & N/A & Interacting with Docker and Singularity containers \\
		dynbenchmark & aut & Github & N/A & Pipeline for benchmarking trajectory inference methods \\
		dyndimred & aut & CRAN & 560 & Applying dimensionality reduction methods \\
		dyneval & aut & Github & N/A & Evaluating trajectory inference methods \\
		dynfeature & aut & Github & N/A & Calculating feature importance scores from trajectories \\
		dyngen & aut & Github & N/A & Simulating single-cell data using gene regulatory networks \\
		dynguidelines & aut & Github & N/A & User guidelines for trajectory inference \\
		dynmethods & aut & Github & N/A & A collection of wrappers for trajectory inference methods \\
		dyno & aut & Github & N/A & A pipeline for inferring, visualising and interpreting trajectories \\
		dynparam & aut & CRAN & 790 & Creating meta-information for parameters \\
		dynplot & aut & Github & N/A & A simple visualisation library for trajectories \\
		dynplot2 & aut & Github & N/A & A fully customisable visualisation library for trajectories \\
		dyntoy & aut & Github & N/A & Generating simple toy data of cellular differentiation \\
		dynutils & aut & CRAN & 7143 & Common functionality for the dynverse packages \\
		dynwrap & aut & Github & N/A & A common format for trajectories \\
		GillespieSSA & aut & CRAN & 5260 & Gillespie's Stochastic Simulation Algorithm (SSA) \\
		GillespieSSA2 & aut & CRAN & N/A & Gillespie's Stochastic Simulation Algorithm for Impatient People \\
		gng & aut & Github & N/A & An Rcpp implementation of the Growing Neural Gas algorithm \\
		incgraph & aut & CRAN & 2863 & Incremental graphlet counting for network optimisation \\
		princurve & aut & CRAN & 27'589 & Fits a principal curve in arbitrary dimension \\
		proxyC & aut & CRAN & 3861 & Computes proximity in large sparse matrices \\
		qsub & aut & CRAN & 3273 & Running commands remotely on gridengine clusters \\
		SCORPIUS & aut & CRAN & 3448 & Inferring developmental chronologies from single-cell RNA sequencing data \\ \hline\hline
		Clus\-ter\-Sig\-nif\-i\-cance & ctb & Bioc & 1553 & Assess if class clusters in dimensionality reduced data representations have a separation different from permuted data \\
		devtools & ctb & CRAN & 4'711'985 & Tools to make developing R packages easier \\
		merlot & ctb & Github & N/A & A method for reconstructing lineage-tree topologies from scRNA-seq data \\
		mlr & ctb & CRAN & 145'913 & Machine Learning in R \\
		monocle & ctb & Bioc & 38'555 & Clustering, differential expression, and trajectory analysis for single-cell RNA-Seq \\
		ParamHelpers & ctb & CRAN & 125'471 & Helpers for Parameters in Black-Box Optimization, Tuning and Machine Learning \\
		pseudogp & ctb & Github & N/A & Probabilistic pseudotime for single-cell RNA-seq \\
		remotes & ctb & CRAN & 2'019'623 & R package installation from remote repositories, including GitHub \\
		rlang & ctb & CRAN & 9'838'123 & Functions for base types and core R and tidyverse features \\
		SCope & ctb & Github & N/A & Visualization of large-scale and high dimensional single cell data \\
		slingshot & ctb & Bioc & 3772 & Tools for ordering single-cell sequencing \\
		splatter & ctb & Bioc & 5360 & Simple simulation of single-cell RNA sequencing data \\
		URD & ctb & Github & N/A & URD reconstructs transcriptional trajectories underlying specification or differentiation processes in the form of a branching tree from single-cell RNAseq data \\
		wishbone & ctb & Github & N/A & Identify bifurcating developmental trajectories from single-cell data \\\hline
	\end{tabularx}
\end{table}

>>>>

\newcommand{\cranpkg}[1]{\href{https://cran.r-project.org/package=#1}{#1}}
\newcommand{\biocpkg}[1]{\href{https://bioconductor.org/packages/#1}{#1}}
\newcommand{\biocpkgl}[2]{\href{https://bioconductor.org/packages/#1}{#2}}
\newcommand{\githubpkg}[2]{\href{https://github.com/#1/#2}{#2}}

@@

	\centering\fontsize{9}{11}\selectfont
	\begin{tabularx}{\linewidth}{|p{2cm}lllX|}
		\hline
		Name & Role & Host & Downloads p.a. & Description \\ \hline\hline
		\cranpkg{babelwhale} & aut & CRAN & N/A & Interacting with Docker and Singularity containers \\
		\githubpkg{dynverse}{dynbenchmark} & aut & Github & N/A & Pipeline for benchmarking trajectory inference methods \\
		\cranpkg{dyndimred} & aut & CRAN & 560 & Applying dimensionality reduction methods \\
		\githubpkg{dynverse}{dyneval} & aut & Github & N/A & Evaluating trajectory inference methods \\
		\githubpkg{dynverse}{dynfeature} & aut & Github & N/A & Calculating feature importance scores from trajectories \\
		\githubpkg{dynverse}{dyngen} & aut & Github & N/A & Simulating single-cell data using gene regulatory networks \\
		\githubpkg{dynverse}{dynguidelines} & aut & Github & N/A & User guidelines for trajectory inference \\
		\githubpkg{dynverse}{dynmethods} & aut & Github & N/A & A collection of wrappers for trajectory inference methods \\
		\githubpkg{dynverse}{dyno} & aut & Github & N/A & A pipeline for inferring, visualising and interpreting trajectories \\
		\cranpkg{dynparam} & aut & CRAN & 790 & Creating meta-information for parameters \\
		\githubpkg{dynverse}{dynplot} & aut & Github & N/A & A simple visualisation library for trajectories \\
		\githubpkg{dynverse}{dynplot2} & aut & Github & N/A & A fully customisable visualisation library for trajectories \\
		\githubpkg{dynverse}{dyntoy} & aut & Github & N/A & Generating simple toy data of cellular differentiation \\
		\cranpkg{dynutils} & aut & CRAN & 7143 & Common functionality for the dynverse packages \\
		\githubpkg{dynverse}{dynwrap} & aut & Github & N/A & A common format for trajectories \\
		\cranpkg{GillespieSSA} & aut & CRAN & 5260 & Gillespie's Stochastic Simulation Algorithm (SSA) \\
		\cranpkg{GillespieSSA2} & aut & CRAN & N/A & Gillespie's Stochastic Simulation Algorithm for Impatient People \\
		\githubpkg{dynverse}{gng} & aut & Github & N/A & An Rcpp implementation of the Growing Neural Gas algorithm \\
		\cranpkg{incgraph} & aut & CRAN & 2863 & Incremental graphlet counting for network optimisation \\
		\cranpkg{princurve} & aut & CRAN & 27'589 & Fits a principal curve in arbitrary dimension \\
		\cranpkg{proxyC} & aut & CRAN & 3861 & Computes proximity in large sparse matrices \\
		\cranpkg{qsub} & aut & CRAN & 3273 & Running commands remotely on gridengine clusters \\
		\cranpkg{SCORPIUS} & aut & CRAN & 3448 & Inferring developmental chronologies from single-cell RNA sequencing data \\ \hline\hline
		\biocpkgl{ClusterSignificance}{Clus\-ter\-Sig\-nif\-i\-cance} & ctb & Bioc & 1553 & Assess if class clusters in dimensionality reduced data representations have a separation different from permuted data \\
		\cranpkg{devtools} & ctb & CRAN & 4'711'985 & Tools to make developing R packages easier \\
		\githubpkg{soedinglab}{merlot} & ctb & Github & N/A & A method for reconstructing lineage-tree topologies from scRNA-seq data \\
		\cranpkg{mlr} & ctb & CRAN & 145'913 & Machine Learning in R \\
		\biocpkg{monocle} & ctb & Bioc & 38'555 & Clustering, differential expression, and trajectory analysis for single-cell RNA-Seq \\
		\cranpkg{ParamHelpers} & ctb & CRAN & 125'471 & Helpers for Parameters in Black-Box Optimization, Tuning and Machine Learning \\
		\githubpkg{kieranrcampbell}{pseudogp} & ctb & Github & N/A & Probabilistic pseudotime for single-cell RNA-seq \\
		\cranpkg{remotes} & ctb & CRAN & 2'019'623 & R package installation from remote repositories, including GitHub \\
		\cranpkg{rlang} & ctb & CRAN & 9'838'123 & Functions for base types and core R and tidyverse features \\
		\githubpkg{aertslab}{SCope} & ctb & Github & N/A & Visualization of large-scale and high dimensional single cell data \\
		\biocpkg{slingshot} & ctb & Bioc & 3772 & Tools for ordering single-cell sequencing \\
		\biocpkg{splatter} & ctb & Bioc & 5360 & Simple simulation of single-cell RNA sequencing data \\
		\githubpkg{farrelja}{URD} & ctb & Github & N/A & URD reconstructs transcriptional trajectories underlying specification or differentiation processes in the form of a branching tree from single-cell RNAseq data \\
		\githubpkg{ManuSetty}{wishbone} & ctb & Github & N/A & Identify bifurcating developmental trajectories from single-cell data \\\hline
	\end{tabularx}
\end{table}
